Analysis File and R Plots

### 2018-11-29 Visualizations/Draft Visualizations Template.Rmd
Update Files

---
title: "Draft Visualizations for Semester Project"
output: word_document
---

@@

```{r}
t7 <- ggplot(health, aes(x = health$pd3))+geom_bar()+facet_wrap( health$Does.your.employer.offer.resources.to.learn.more.about.mental.health.concerns.and.options.for.seeking.help. ~., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Mental Health Resource Provision") + xlab("Perceived Difficulty Level") + ylab("Count")
t7
```
NOTE:  VE = Very Easy, SE = Somewhat Easy, N = Neutral (or Neither Easy nor Difficult), SH = Somewhat Hard, VH = Very Hard, DK = Don't Know.

@@

```{r}
t12 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s..))+geom_bar()+facet_wrap(health$negimp ~., scales="free_y") + ggtitle("Comfort with Discussing MH with Supervisor by Perception of Negative Impact") + xlab("Would you feel comfortable discussing a mental health disorder with your supervisor?") + ylab("Count")
t12
```

@@

```{r}
t13 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers.))+geom_bar()+facet_wrap(health$gender ~., scales="free_y") + ggtitle("Comfort with Discussing MH with Coworkers by Gender") + xlab("Would you feel comfortable discussing a mental health disorder with your coworkers?") + ylab("Count")
t13
```

@@

```{r}
t16 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers.))+geom_bar()+facet_wrap(health$Have.you.observed.or.experienced.an.unsupportive.or.badly.handled.response.to.a.mental.health.issue.in.your.current.or.previous.workplace. ~., scales="free_y") + ggtitle("Comfort Discussing MH w/ Coworkers by Exp. w/ Poor Workplace MH Response") + xlab("Would you feel comfortable discussing a mental health disorder with your coworkers?") + ylab("Count")
t16
```

@@

```{r}
t17 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers.))+geom_bar()+facet_wrap(health$Do.you.think.that.team.members.co.workers.would.view.you.more.negatively.if.they.knew.you.suffered.from.a.mental.health.issue. ~., scales="free_y") + ggtitle("Comfort with Discussing MH with Coworkers by Perceived Negative Impact") + xlab("Would you feel comfortable discussing a mental health disorder with your coworkers?") + ylab("Count")
t17
```

>>>>

---
title: "Analysis File and R Plots"
output: word_document
---

@@

```{r}
t7 <- ggplot(health, aes(x = health$pd3))+geom_bar()+facet_wrap( health$Does.your.employer.offer.resources.to.learn.more.about.mental.health.concerns.and.options.for.seeking.help. ~., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by MH Resource Provision") + xlab("Perceived Difficulty Level") + ylab("Count")
t7
```
NOTE:  VE = Very Easy, SE = Somewhat Easy, N = Neutral (or Neither Easy nor Difficult), SH = Somewhat Hard, VH = Very Hard, DK = Don't Know.

@@

```{r}
t12 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s..))+geom_bar()+facet_wrap(health$negimp ~., scales="free_y") + ggtitle("Comfort with Discussing MH with Supervisor by Perceived Negative Impact") + xlab("Would you feel comfortable discussing a mental health disorder with your supervisor?") + ylab("Count")
t12
```

@@

```{r}
t13 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers.))+geom_bar()+facet_wrap(health$gender ~., scales="free_y") + ggtitle("Comfort with Discussing MH with Coworkers by Gender") + xlab("Would you feel comfortable discussing a MH disorder with your coworkers?") + ylab("Count")
t13
```

@@

```{r}
t16 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers.))+geom_bar()+facet_wrap(health$Have.you.observed.or.experienced.an.unsupportive.or.badly.handled.response.to.a.mental.health.issue.in.your.current.or.previous.workplace. ~., scales="free_y") + ggtitle("Comfort Discuss MH w/ Coworkers by Exp. w/ Poor Workplace MH Response") + xlab("Would you feel comfortable discussing a mental health disorder with your coworkers?") + ylab("Count")
t16
```

@@

```{r}
t17 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers.))+geom_bar()+facet_wrap(health$Do.you.think.that.team.members.co.workers.would.view.you.more.negatively.if.they.knew.you.suffered.from.a.mental.health.issue. ~., scales="free_y") + ggtitle("Comfort Discussing MH with Coworkers by Perceived Negative Impact") + xlab("Would you feel comfortable discussing a mental health disorder with your coworkers?") + ylab("Count")
t17
```
